Reassessing the Impact of Dynamic Slicing in SFL

### 2019-02-11 paper/ijcai/paper.tex
oracle heuristics + object of analysis + methodology pass

Our implementation of Critical Slicing is based on the Mozilla Lithium
tool~\cite{lithium}. Lithium implements the DD-min Delta Debugging
algorithm~\cite{zeller-hildebrandt-tse2002}. It takes as input a file
and produces as output a simplified version of that file that
satisfies a user-defined oracle. In our case, the oracle is defined
such that the test produces the same failure manifestation as the one
observed with the test execution on the original program. The
Lithium minimization process starts by determining the initial size---in number of lines---of
chunks to delete from the input file. For that,
it chooses the highest power of two number smaller than the file
size. For example, if the file has 1,000 lines, Lithium sets the
initial chunk size to 512 lines. Then, the tool starts a local search looking 
for chunks to exclude from the file. If the chunk satisfies the oracle it is removed. 
When no more chunks of that given size can be removed, Lithium
divides the chunk size by two and repeats the search. This iterative
process continues until no more lines can be removed.  If $n$ is the
size of the input file and $m$ is the size of the 1-minimal file found
by Lithium, then Lithium usually performs $O(m\cdot\lg(n))$
iterations. Proofs of the algorithm complexity can be found
elsewhere~\cite{lithium-complexity}. Our implementation is publicly
available.

@@

Lithium takes as input a function of interest that can be designed according to the problem to be solved. The function of interest determines if the test case output is interesting or not. In this study, interesting means that the test execution path is equal to the expected one. This information can be deducted from the defects stack traces which show the stack of functions called until the thrown of an exception. The authors assume that it is only necessary to compare both stack traces until the call where the test fails. For each chunk under evaluation, the test is executed without considering the chunk under evaluation (Algorithm \ref{alg:finc}, line 2). Both test ($testStk$) and expected ($expStk$) stack traces are filtered according to the position of the test call fails. These operations are performed by line 3 and 4 from Algorithm 2. Finally, both messages are compared and if equal the chunk will be deleted from the project, i.e., the chunk is not interesting to reveal the fault of the test.

 (Algorithm \ref{alg:finc})

@@

%This section evaluates \comb{}.

\subsection{Objects of Analysis}

As in other recent related studies, we used the \dfj{} benchmark in
our experiments~\cite{just-defects4j-issta2014}. The \dfj{} benchmark
includes six subjects and \numFaults{} faults (Table \ref{tab:df4j}).
\lang{} is a library that provides a set of helper utilities for the
     {\small\texttt{java.lang}} API. \cmath{} is a lightweight library
     of self-contained mathematics and statistics components. The
     \closure{} is a toolset for turning JavaScript files into smaller
     scripts for faster download and execution in the
     browser. \chart{} is a Java library for creating charts. \jtime{}
     is a lightweight library that aims to replace the default Java
     {\small\texttt{java.util.Date}} classes providing simpler
     APIs. \mockito{} is a mocking testing framework.\comments{ that
       enables the developer to simulate the behavior of classes that
       cannot be used in unit testing.}

\newcommand{\cgray}[1]{\cellcolor{gray!25}#1}
\begin{table}[h]
  \centering
  \setlength{\tabcolsep}{4pt}
    \begin{tabular}{lrrr}
      \toprule
      Project            & Size (kLOC) & \# Tests & \# Faults \\ %\comments{& Failing Test Cases &}
      \midrule
      \lang{}            & 111751  & 6057 & 65       \\   %\commentst{& 124   &  -}\\
      \cmath{}           & 306276  & 26797 & 106     \\   %\comments{& 177   &  -}\\
      \closure{}         & 149521  & 27930  & 133     \\   %\comments{& 350   &  -}\\
      \chart{}           & 230159  & 8458 & 26      \\  %\comments{& 92    &  -}\\
      \jtime{}           & 141610  & 3289 & 27       \\   %\comments{& 76    &  -}\\
      \mockito{}         & 22787  & 8835 & 38    \\     %\comments{& 118   &  -}\\
      \bottomrule
  \end{tabular}
\caption {Characterization of \dfj{} subjects.\Mar{numbers seem too
    big. is this really in
    *k*LOC or just LOC? please, confirm.}\Sof{I think it is a mistake and the unit should be LOC. But I will check.}}
\label{tab:df4j}
\end{table}
\normalsize

@@

\subsection{Methodology}

The evaluation techniques are SFL and \comb{}-$k$, for
$k\in\{5,10\}$. \Mar{Simplified and moved this par. from Section
  4.0. I noticed you used this terminology (\comb{} with ``-k'')
  below. Please, explain and provide rationale}.\Sof{Not sure if it is the right one, an alterantive is using only SFL+DS
  and instead of top-5 and top-10 use K = 5 and K = 10... Which do you think is the best?}

To be able to effectively compare \comb{}-k against SFL, we first reduce the SFL report to method components. This reduction is done by considering the highest fault probability of the top-k components of each fault (/subject), to effectively be able to compare method-level diagnostic effort between the
two approaches. A variety in diagnostic effort is measured
using\Sof{@todo: revise it, it is confusing}

@@

where C is the cost of diagnosis. \Sof{@todo: Need to explain this better}
A positive $\Delta$C means that the faulty component has risen in
the ranking reported by SFL techniques when DS is used,
yielding a lowered cost of diagnosing.

>>>>

Our implementation of Critical Slicing is based on the Mozilla Lithium
tool\footnote{Lithium details available at \url{https://github.com/MozillaSecurity/lithium} (Accessed on \today)}. Lithium implements the DD-min Delta Debugging
algorithm~\cite{zeller-hildebrandt-tse2002}. It takes as input a file
and produces as output a simplified version of that file that
satisfies a user-defined oracle. In our case, the oracle is defined
such that the test produces the same failure manifestation as the one
observed with the test execution on the original program. The
Lithium minimization process starts by determining the initial size---in number of lines---of
chunks to delete from the input file. For that,
it chooses the highest power of two number smaller than the file
size. For example, if the file has 1,000 lines, Lithium sets the
initial chunk size to 512 lines. Then, the tool starts a local search looking 
for chunks to exclude from the file. If the chunk satisfies the oracle it is removed. 
When no more chunks of that given size can be removed, Lithium
divides the chunk size by two and repeats the search. This iterative
process continues until no more lines can be removed.  If $n$ is the
size of the input file and $m$ is the size of the 1-minimal file found
by Lithium, then Lithium usually performs $O(m\cdot\lg(n))$
iterations. Proofs of the algorithm complexity can be found
elsewhere\footnote{Lithium complexity available at \url{https://github.com/MozillaSecurity/lithium/blob/master/src/lithium/docs/algorithm.md} (Accessed on \today)}. Our implementation is publicly
available.

@@

Lithium takes as input a function of interest that can be designed according to the problem to be solved. The function of interest determines if the test case output is interesting or not. In this study, interesting means that the test execution path is equal to the expected one. This information can be deducted from the defects stack traces which show the stack of functions called until the thrown of an exception. The interesting function compares both stack traces (from the test under evaluation and the expected one) until the call where the test fails. For each chunk under evaluation, the test is executed after the chunk being deleted from the source code (Algorithm \ref{alg:finc}, line 2). Both test ($testStk$) and expected ($expStk$) stack traces are filtered. We only consider stack traces until the line where the main exception is launched. These operations are performed by line 3 and 4 from Algorithm 2. Finally, both messages are compared and if equal the chunk will be deleted from the project, i.e., the chunk is not interesting to reveal the fault of the test.

@@

To evaluate our approach, we compare the cost of diagnosing
a collection of faulty versions using \sfl{}
against \comb{}.

\subsection{Objects of Analysis}\label{sec:analysis}

As in other recent related studies, we used the \dfj{} benchmark in
our experiments~\cite{just-defects4j-issta2014}. The \dfj{} benchmark
includes six different subjects and \numFaults{} faults (Table \ref{tab:df4j}).
\lang{} is a library that provides a set of helper utilities for the
     {\small\texttt{java.lang}} API. \cmath{} is a lightweight library
     of self-contained mathematics and statistics components. The
     \closure{} is a toolset for turning JavaScript files into smaller
     scripts for faster download and execution in the
     browser. \chart{} is a Java library for creating charts. \jtime{}
     is a lightweight library that aims to replace the default Java
     {\small\texttt{java.util.Date}} classes providing simpler
     APIs. \mockito{} is a mocking testing framework.\comments{ that
       enables the developer to simulate the behavior of classes that
       cannot be used in unit testing.}

\newcommand{\cgray}[1]{\cellcolor{gray!25}#1}
\begin{table}[h]
  \centering
  \setlength{\tabcolsep}{4pt}
    \begin{tabular}{lrrr}
      \toprule
      Project            & Size (LOC) & \# Tests & \# Faults \\ %\comments{& Failing Test Cases &}
      \midrule
      \lang{}            & 111751  & 6057 & 65       \\   %\commentst{& 124   &  -}\\
      \cmath{}           & 306276  & 26797 & 106     \\   %\comments{& 177   &  -}\\
      \closure{}         & 149521  & 27930  & 133     \\   %\comments{& 350   &  -}\\
      \chart{}           & 230159  & 8458 & 26      \\  %\comments{& 92    &  -}\\
      \jtime{}           & 141610  & 3289 & 27       \\   %\comments{& 76    &  -}\\
      \mockito{}         & 22787  & 8835 & 38    \\     %\comments{& 118   &  -}\\
      \bottomrule
  \end{tabular}
\caption {Characterization of \dfj{} subjects.\Sof{Use SLOCCount to count size}}
\label{tab:df4j}
\end{table}
\normalsize

@@

\subsection{Methodology}\label{sec:methodology}

The main goal of our evaluation is to understand what is the impact of \ds{} on 
\sfl{} after minimizing the $k$ highest faulty source files which comprise the highest faulty statements. Firstly, we ran the dataset presented in Section~\ref{sec:analysis} with \sfl{} to 
gather the coverage statements ordered from the highest faulty statement to the
lowest faulty statement. This list is the input of the \comb{} technique. For each defect, the list is evaluated in order to get the top-$k$, for $k\in\{5,10\}$, of suspicious source files. Then, Lithium minimizes each source file for each testcase of the defect considering the top-$5$ (\comb{}-$5$) and top-$10$ (\comb{}-$10$) of source files separately. Some defects have more than one testcase. In the end, we update spectra $S$ based on the output of the minimization as presented in Figure~\ref{fig:ds-reduction} to obtain the faulty statements ranking after minimization. All scripts used to run these experiments and gather data are available at \url{TBA} and \url{TBA}, respectively.

We perform experiments for \comb{}-$5$ and \comb{}-$10$. These techniques results are analyzed against \sfl{}. The difference in the diagnostic effort is measured
using

@@

where C is the cost of diagnosis. \Sof{@todo: Explain this better in section 2 or 3}
A positive $\Delta$C means that the faulty statement has risen in
the ranking reported by \sfl{} techniques when \ds{} is used,
producing a reduced cost of diagnosing.
